Observed vs. Simulated Year Comparison

### 2023-10-19 03-post-process/compare-sim-to-obs.Rmd
Replace all instances of %>% with |>
Native pipe operator

  kable(table_x, "html", digits = 2, row.names = FALSE, align = "llllccccc") %>%
    kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    column_spec(5, background = assign_color(x[,5])) %>%
    column_spec(6, background = assign_color(x[,6])) %>%
    column_spec(7, background = assign_color(x[,7])) %>%
    column_spec(8, background = assign_color(x[,8])) %>%
    column_spec(9, background = assign_color(x[,9])) %>%
    collapse_rows(1:4)
}
```

>>>>

  kable(table_x, "html", digits = 2, row.names = FALSE, align = "llllccccc") |> 
    kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
    column_spec(5, background = assign_color(x[,5])) |> 
    column_spec(6, background = assign_color(x[,6])) |> 
    column_spec(7, background = assign_color(x[,7])) |> 
    column_spec(8, background = assign_color(x[,8])) |> 
    column_spec(9, background = assign_color(x[,9])) |> 
    collapse_rows(1:4)
}
```

### 2023-10-19 03-post-process/ms-content/ms-content.Rmd
Replace all instances of %>% with |>
Native pipe operator

# create the table
kbl(tab, format = "latex", booktabs = TRUE, longtable = FALSE, linesep = "", caption = "Time elapsed in calculating the content in this document.") %>%
  kable_styling(full_width = FALSE, latex_options = "HOLD_position") %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, monospace = TRUE) %>%
  row_spec(nrow(tab), bold = TRUE)
```

>>>>

# create the table
kbl(tab, format = "latex", booktabs = TRUE, longtable = FALSE, linesep = "", caption = "Time elapsed in calculating the content in this document.") |> 
  kable_styling(full_width = FALSE, latex_options = "HOLD_position") |> 
  row_spec(0, bold = TRUE) |> 
  column_spec(1, monospace = TRUE) |> 
  row_spec(nrow(tab), bold = TRUE)
```

### 2023-10-19 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Replace all instances of %>% with |>
Native pipe operator

# print a table 
kable(t(est), digits = 0, format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
```

>>>>

# print a table 
kable(t(est), digits = 0, format.args = list(big.mark = ",")) |> 
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed", "striped"))
```

### 2023-10-19 03-post-process/output-plots-children/11-residual-diags.Rmd
Replace all instances of %>% with |>
Native pipe operator

  # make the table
  knitr::kable(out_values, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    column_spec(5, background = out_colors[,5]) %>%
    column_spec(6, background = out_colors[,6]) %>%
    column_spec(7, background = out_colors[,7]) %>%
    column_spec(8, background = out_colors[,8]) %>%
    column_spec(9, background = out_colors[,9]) %>%
    collapse_rows(columns = 1:4)
}
```

@@

  knitr::kable(out_values, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    column_spec(6, background = out_colors[,6]) %>%
    column_spec(7, background = out_colors[,7]) %>%
    column_spec(8, background = out_colors[,8]) %>%
    column_spec(9, background = out_colors[,9]) %>%
    column_spec(10, background = out_colors[,10]) %>%
    collapse_rows(columns = 1:5)
}
```

>>>>

  # make the table
  knitr::kable(out_values, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") |>
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
    column_spec(5, background = out_colors[,5]) |> 
    column_spec(6, background = out_colors[,6]) |> 
    column_spec(7, background = out_colors[,7]) |> 
    column_spec(8, background = out_colors[,8]) |> 
    column_spec(9, background = out_colors[,9]) |> 
    collapse_rows(columns = 1:4)
}
```

@@

  knitr::kable(out_values, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") |> 
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) |> 
    column_spec(6, background = out_colors[,6]) |> 
    column_spec(7, background = out_colors[,7]) |> 
    column_spec(8, background = out_colors[,8]) |> 
    column_spec(9, background = out_colors[,9]) |> 
    column_spec(10, background = out_colors[,10]) |> 
    collapse_rows(columns = 1:5)
}
```

### 2023-10-19 03-post-process/output-plots-children/99-waic.Rmd
Replace all instances of %>% with |>
Native pipe operator

waic_out = as.data.frame(as.list(waic_out))
waic_out %>%
  kbl(format.args = list(big.mark = ",")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
```

>>>>

waic_out = as.data.frame(as.list(waic_out))
waic_out |> 
  kbl(format.args = list(big.mark = ",")) |> 
  kable_styling(full_width = FALSE, bootstrap_options = c("condensed"))
```
